Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)

### 2020-05-21 doc/paper.tex
update docs

It is clear that neutrinos carry the peculiar mass smaller than $\mathcal{O}(1)$ eV among elementary particles, although the absolute value of each neutrino mass is unknown. In addition, one of the fundamental questions with regards to neutrino properties is how neutrino masses are generated naturally. 
%The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector with the help of neutrino flavor mixings. 
The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector. 
%Anyhow new particles have to be introduced in such a mechanism. 
More degrees of freedom in a theoretical model, the less predictivity of observables in experiments. Furthermore, flavour symmetries are employed to reduce degrees of freedom in the neutrino mass model. These models can explain the origin of the neutrino mixing, and predict correlations of oscillation parameters (some of recent review articles are~\cite{Altarelli:2010gt,Ishimori:2010au,King:2013eh,King:2014nza,King:2015aea,King:2015ata,King:2017guk}). Before the discovery of non-zero $\theta_{13}$ by Daya Bay reactor neutrino experiment~\cite{An:2013zwz}, the `tri-bi-maximal' neutrino mixing (TBM) ansatz, which was proposed in 2002 by Horrison, Perkins, and Scott~\cite{Harrison:2002er}, was in line with experimental data:
\begin{equation*}
U_{\text{TBM}}=\left(
\begin{array}{ccc}
2/\sqrt{6} & 1/\sqrt{3} & 0\\
-1/\sqrt{6} & 1/\sqrt{3} & 1/\sqrt{2}\\
1/\sqrt{6}  & -1/\sqrt{3} & 1/\sqrt{2}
\end{array}\right).
\end{equation*} 
Given $\theta_{13}\approx 8^\circ$ measured by several reactor neutrino experiments, we have to break this mixing pattern to to obtain such non-zero value of $\theta_{13}$. One of popular proposals is to correct the tri-bi-maximal neutrino mixing such that 
\begin{equation*}
\sin\theta_{12}=(1+s)/\sqrt{3},~\sin\theta_{13}=r/\sqrt{2},~\text{and}~\sin\theta_{23}=(1+a)/\sqrt{2}.
\end{equation*}
It is relatively easy for model builders to check the validity of the neutrino mass model and constrain model parameters by the public NUFIT results \cite{Esteban:2018azc}. However, there is no such a public toolkit to evaluate model predictions in future neutrino experiments. \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \cite{Huber:2004ka,Huber:2007ji} is a convenient tool to simulate neutrino oscillation experiments via the Abstract Experiment Definition Language (AEDL) as one of the most popular and powerful tools in the community of neutrino oscillation physics. Some AEDL files to describe experiments are also available in \textbf{GLoBES} website, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in a AEDL file, provided in~\cite{Alion:2016uaj}. It is to be extended for the purpose of analysing flavour symmetry models in an universal way.

@@

The user can use \textbf{FaSE-GLoBES} to constrain model parameters. 
{\color{blue}Suppose we have the measurement $\vec{x}$ and the likelihood function $L(\vec{\theta})=P(\vec{x}|\vec{\theta})$ for a set of parameters $\vec{\theta}=(\theta_1,...,\theta_N)$, where $P(\vec{x}|\vec{\theta})$ is the probability function for data $\vec{x}$ in favour of the hypothesis $\vec{\theta}$. The constraint of model parameters can be obtained with the statistis parameter $\chi^2\equiv \ln L(\vec{\theta})$.}
The expression $\chi^2$ is used as the default \textbf{GLoBES} setting. \textcolor{red}{[JT: What is the meaning of this $\chi^2$ here?]} In more detail, the $\chi^2$ function{\color{blue}, following the Poisson distribution,} is constructed based on a log-likelihood ratio,
%\begin{equation}\label{eq:chi-squared}
\begin{align}\label{eq:chi-squared}
\chi^2(\vec{\theta}^{hyp},\xi_s,\xi_b)=&2\sum_i\left(\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)-n_i+n_i\ln\frac{n_i}{\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)} \right)\nonumber\\
&+p(\xi_s,\sigma_s)+p(\xi_b,\sigma_b)+\chi^2_{prior},
\end{align}
%\end{equation}
where $i$ runs over the number of bins, $\eta_i(\vec{\theta},\xi_s,\xi_b)$ is the assumed event rate in the $i$th bin and $E_i$ is the central value in this energy bin. The vector $\vec{\theta}$ consists of model or oscillation parameters. The parameters $\xi_s$ and $\xi_b$ are introduced to account for the systematic uncertainties in the normalisation for the signal (subscript $_s$) and background (subscript $_b$) components of the event rate, and are allowed to vary in the fit as nuisance parameters. For a given set of parameters $\vec{\theta}$, the event rate in the $i$th energy bin is calculated as\\
\begin{equation}
\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)=(1+\xi_s)\times s_i+(1+\xi_b)\times b_i,
\end{equation}
where $s_i$ and $b_i$ are the expected number of signal and background events in $i$th energy bin, respectively. The nuisance parameters are constrained by the Gaussian prior $p(\xi,\sigma)=\xi^2/\sigma^2$ with corresponding uncertainties $\sigma_s$ and $\sigma_b$ for the signal and background, respectively. Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~(\ref{eq:prior}). After doing all minimisations, the user obtain the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp}$, $\chi^2(\vec{\theta}^{hyp})$.

Based on the $\chi^2$ function Eq.~(\ref{eq:chi-squared}), we can study how model parameters can be constrained and whether a flavour-symmetry neutrino model is excluded by simulated experiments. In the following we will demonstrate with typical examples how it works, {\color{blue} before presenting some demonstrations in next two sections.}

@@

The user of \textbf{FaSE-GLoBES} is able to study how model parameters can be constrained by the simulated experiments. To do so, the user needs to simulate the true event spectrum $n_i$ with a set of model ($\vec{\theta}_{Model}^{true}$) or oscillation parameters ($\vec{\theta}_{OSC}^{true}$), \textit{i.e.}~set up $n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC}^{true})$. The hypothesis $\vec{\theta}_{Model}^{hyp}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp},\xi_s,\xi_b)$. With the default settings for $\chi^2$ function as Eq.~(\ref{eq:prior}) in \textbf{FaSE-GLoBES}, the user computes the statistical quantity,
\begin{equation}\label{eq:chi_model}
\chi^2(\vec{\theta}_{Model}^{hyp}),~~\text{with}~n_i(\vec{\theta}_{Model}^{true})~\text{or}~n_i(\vec{\theta}_{OSC}^{true}).
\end{equation}
%
We note that the minimum of $\chi^2$ in the whole parameter space ($\chi^2_{min.}$) may not be $0$. Therefore, to get the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})\equiv \chi^2(\vec{\theta}_{Model}^{hyp})-\chi^2_{min.}$, instead of $\chi^2$ itself. By varying different hypotheses $\vec{\theta}_{Model}^{hyp}$, we will obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})$.

The user can also study how well a flavour symmetry model explains the computed data, or predict whether the simulated experiment can exclude this model or not. In other words, the user studies the minimum of $\chi^2$ for the flavour symmetry model $\vec{\theta}_{Model}$ as a hypothesis, by assuming different true oscillation values, \textit{i.e.}~different $\vec{\theta}^{true}_{OSC}$. To do so, one can compute the same statistical quantity Eq.~(\ref{eq:chi_model}), while the true spectrum is varied with different true values $\vec{\theta}_{OSC}^{true}$. All model parameters are allowed to be varied with the user-defined prior.
%
Finally, the user might adopt Wilk's theorem to interpret results~\cite{Wilks:1938dza}. When we compare nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed as a $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters \texttt{dof}.

@@

\textbf{FaSE-GloBES} can be used to study how model parameters are constrained by simulated neutrino oscillation experiments. We take \textit{the tri-direct littlest seesaw} (TDLS)~\cite{King:2013iva,King:2015dvf,King:2016yvg} as an example. In this model, the light left-handed Majorana neutrino mass matrix is given by
\begin{equation}
\label{eq:mnu}  m_{\nu}=m_{a}\begin{pmatrix}
 1 &~ \omega  &~ \omega ^2 \\
 \omega  &~ \omega ^2 &~ 1 \\
 \omega ^2 &~ 1 &~ \omega  \\
\end{pmatrix}+e^{i\eta}m_{s}
\begin{pmatrix}
 1 &~  x &~  x \\
 x &~ x^2 &~ x^2 \\
 x &~ x^2 &~ x^2 \\
\end{pmatrix}\,,
\end{equation}
where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters to be constrained by simulated data. We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FaSE-GLoBES}. Therefore, the restrictions in this model are $m_a>0$ and $r>0$.
%\begin{figure}[!h]
% \flushleft
%\hspace{15mm}\includegraphics[width=0.32\textwidth]{figs/x_eta.pdf}$~~~~~~$\\
%\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_r.pdf}\hspace{-11mm}
% \includegraphics[width=0.32\textwidth]{figs/eta_r.pdf}$~~~~~~$\\
%\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_ma.pdf}\hspace{-11mm}
% \includegraphics[width=0.32\textwidth]{figs/eta_ma.pdf}\hspace{-11mm}
% \includegraphics[width=0.32\textwidth]{figs/r_ma.pdf}
% \caption{\label{fig:model_2D}Precision measurements of any two model parameters at 3$\sigma$ confidence level in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black). True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
%\end{figure}

\begin{figure}[!h]
 %\flushleft
 \centering
\includegraphics[width=0.48\textwidth]{Figs/x_eta.pdf}
 \includegraphics[width=0.48\textwidth]{Figs/theta_phi.pdf}
% \caption{\label{fig:constraint}Precision measurements of two model parameters in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black). True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
 %
  \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw (left) and the warped flavor symmetry (right), with simulated DUNE and MOMENT data.}
\end{figure}

In left panel of Fig.~\ref{fig:constraint}, we study how parameters $x$ and $\eta$ can be constrained by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea}. 
%We input the model by giving model parameters as functions of standard oscillation parameters Eq.~(\ref{eq:modelofOSC}). 
Parameters $r$ and $ma$ are varied with the prior that is given in standard oscillation parameters, according to the global-fit result NUFIT4.0. More details are presented in the user manual. 
%The code for this example is provided as \textbf{x\_eta.c} in the \textbf{FaSE} distribution.

@@

{\color{blue}To show the generality of \textbf{FaSE-GLoBES}, we also present the similar result for another model -- \textit{the warped flavor symmetry} (WFS)~\cite{Chen:2015jta}. This model predicts further simplified correlations that the standard oscillation parameters including mixing angles and the CP phase are functions of only two model parameters $\theta_\nu$ and $\phi_\nu$,
\begin{align}\label{eq:WFS}
\sin^2\theta_{12}&=\frac{1}{2-\sin2\theta_{\nu}\cos\phi_\nu},\nonumber\\
\sin^2\theta_{13}&=\frac{1}{3}(1+\sin2\theta_\nu\cos\phi_\nu),\nonumber\\
\sin^2\theta_{23}&=\frac{1-\sin2\theta_\nu\sin(\pi/6-\phi_\nu)}{2-\sin2\theta_\nu\cos\phi_\nu},\nonumber\\
J_{CP}&=-\frac{1}{6\sqrt{3}}\cos2\theta_\nu.
\end{align}
The constraint of $\theta_\nu$ and $\phi_\nu$ for DUNE and MOMENT is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NUFIT 4.0 result as the true values $(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$. To reproduce the result shown in \cite{Chatterjee:2017xkb}, we do not include any priors.}

@@

\begin{figure}[!h]
 \centering
\includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_DUNE_MOMENT.pdf}
\includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_WFS.pdf}
\caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour at $99\%$ C.L. on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS (left) and of WFS (right) with DUNE and MOMENT. }
%\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid). The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results. The black dot denotes the best fit of NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$), while the star is the prediction by the tri-direct littlest seesaw model with NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)\sim(36.25^\circ,~8.63^\circ,~47^\circ,~279^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
\end{figure}

We can also study on whether a neutrino mass model is excluded or not, assuming different true values for oscillation parameters. In this example, we present testing sub-models of TDLS in various true values of $\theta_{23}$ and $\delta$. We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior Eq.~(\ref{eq:prior}) according to NUFIT4.0 results. Two parameters $x$ and $\eta$ are fixed at the best fit. In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code. 
%
{\color{blue}We present this result in the left panel of Fig.~\ref{fig:th23_delta}. We further show the generality of \textbf{FaSE-GLoBES} by demonstrating the similar result for another model -- WFS Eq.~(\ref{eq:WFS}) for DUNE and MOMENT, in right panel of Fig.~\ref{fig:th23_delta}. In this result, two mass-squared differences are fixed at the true values without including any priors.
%
%As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the {\color{blue}assumed} true theory {\color{blue}($\vec{\theta}^{true}_{OSC}$)} and the hypothesis {\color{blue}($\vec{\theta}^{hyp}_{Model}$)}, \texttt{dof}. 
%{\color{blue}`The assumed true theory' here means that the oscillation parameters assumed for predicting the true event spectrum.} \textcolor{red}{[JT: what is the meaning of the true theory?]} 
%Here the number \texttt{dof} is $2$. 
%And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}. \textcolor{red}{[I don't understand this sentence.]} 
More details are presented in the user manual. 
%The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.

}

>>>>

It is clear that neutrinos carry the peculiar mass smaller than $\mathcal{O}(1)$ eV among elementary particles, although the absolute value of each neutrino mass is unknown. In addition, one of the fundamental questions with regards to neutrino properties is how neutrino masses are generated naturally. 
%The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector with the help of neutrino flavor mixings. 
The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector. 
%Anyhow new particles have to be introduced in such a mechanism. 
More degrees of freedom in a theoretical model, the less predictivity of observables in experiments. Furthermore, flavour symmetries are employed to reduce degrees of freedom in the neutrino mass model. These models can explain the origin of the neutrino mixing, and predict correlations of oscillation parameters (some of recent review articles are~\cite{Altarelli:2010gt,Ishimori:2010au,King:2013eh,King:2014nza,King:2015aea,King:2015ata,King:2017guk}). Before the discovery of non-zero $\theta_{13}$ by Daya Bay reactor neutrino experiment~\cite{An:2013zwz}, the `tri-bi-maximal' neutrino mixing (TBM) ansatz, which was proposed in 2002 by Horrison, Perkins, and Scott~\cite{Harrison:2002er}, was in line with experimental data:
\begin{equation*}
U_{\text{TBM}}=\left(
\begin{array}{ccc}
2/\sqrt{6} & 1/\sqrt{3} & 0\\
-1/\sqrt{6} & 1/\sqrt{3} & 1/\sqrt{2}\\
1/\sqrt{6}  & -1/\sqrt{3} & 1/\sqrt{2}
\end{array}\right).
\end{equation*} 
Given $\theta_{13}\approx 8^\circ$ measured by several reactor neutrino experiments, we have to break this mixing pattern to to obtain such non-zero value of $\theta_{13}$. One of popular proposals is to correct the tri-bi-maximal neutrino mixing such that 
\begin{equation*}
\sin\theta_{12}=(1+s)/\sqrt{3},~\sin\theta_{13}=r/\sqrt{2},~\text{and}~\sin\theta_{23}=(1+a)/\sqrt{2}.
\end{equation*}
It is relatively easy for model builders to check the validity of the neutrino mass model and constrain model parameters by the public NuFit results \cite{Esteban:2018azc}. However, there is no such a public toolkit to evaluate model predictions in future neutrino experiments. \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \cite{Huber:2004ka,Huber:2007ji} is a convenient tool to simulate neutrino oscillation experiments via the Abstract Experiment Definition Language (AEDL) as one of the most popular and powerful tools in the community of neutrino oscillation physics. Some AEDL files to describe experiments are also available in \textbf{GLoBES} website, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in a AEDL file, provided in~\cite{Alion:2016uaj}. It is to be extended for the purpose of analysing flavour symmetry models in an universal way.

@@

The user can use \textbf{FaSE-GLoBES} to constrain model parameters. 
Suppose we have the measurement $\vec{x}$ and the likelihood function $L(\vec{\theta})=P(\vec{x}|\vec{\theta})$ for a set of parameters $\vec{\theta}=(\theta_1,...,\theta_N)$, where $P(\vec{x}|\vec{\theta})$ is the probability function for data $\vec{x}$ in favour of the hypothesis $\vec{\theta}$. The constraint of model parameters can be obtained with the statistis parameter $\chi^2\equiv \ln L(\vec{\theta})$.
The expression $\chi^2$ is used as the default \textbf{GLoBES} setting. \textcolor{red}{[JT: What is the meaning of this $\chi^2$ here?]} In more detail, the $\chi^2$ function, following the Poisson distribution, is constructed based on a log-likelihood ratio,
%\begin{equation}\label{eq:chi-squared}
\begin{align}\label{eq:chi-squared}
\chi^2(\vec{\theta}^{hyp},\xi_s,\xi_b)=&2\sum_i\left(\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)-n_i+n_i\ln\frac{n_i}{\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)} \right)\nonumber\\
&+p(\xi_s,\sigma_s)+p(\xi_b,\sigma_b)+\chi^2_{prior},
\end{align}
%\end{equation}
where $i$ runs over the number of bins, $\eta_i(\vec{\theta},\xi_s,\xi_b)$ is the assumed event rate in the $i$th bin and $E_i$ is the central value in this energy bin. The vector $\vec{\theta}$ consists of model or oscillation parameters. The parameters $\xi_s$ and $\xi_b$ are introduced to account for the systematic uncertainties in the normalisation for the signal (subscript $_s$) and background (subscript $_b$) components of the event rate, and are allowed to vary in the fit as nuisance parameters. For a given set of parameters $\vec{\theta}$, the event rate in the $i$th energy bin is calculated as\\
\begin{equation}
\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)=(1+\xi_s)\times s_i+(1+\xi_b)\times b_i,
\end{equation}
where $s_i$ and $b_i$ are the expected number of signal and background events in $i$th energy bin, respectively. The nuisance parameters are constrained by the Gaussian prior $p(\xi,\sigma)=\xi^2/\sigma^2$ with corresponding uncertainties $\sigma_s$ and $\sigma_b$ for the signal and background, respectively. Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~(\ref{eq:prior}). After doing all minimisations, the user obtains the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp}$, $\chi^2(\vec{\theta}^{hyp})$.

Based on the $\chi^2$ function Eq.~(\ref{eq:chi-squared}), we can study how model parameters can be constrained and whether a flavour-symmetry neutrino model is excluded by simulated experiments. In the following we will demonstrate with typical examples how it works, before presenting some demonstrations in next two sections.

@@

The user of \textbf{FaSE-GLoBES} is able to study how model parameters can be constrained by the simulated experiments. To do so, the user needs to simulate the true event spectrum $n_i$ with a set of model ($\vec{\theta}_{Model}^{true}$) or oscillation parameters ($\vec{\theta}_{OSC}^{true}$), \textit{i.e.}~set up $n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC}^{true})$. The hypothesis $\vec{\theta}_{Model}^{hyp}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp},\xi_s,\xi_b)$. With the default settings for $\chi^2$ function as Eq.~(\ref{eq:prior}) in \textbf{FaSE-GLoBES}, the user computes the statistical quantity,
\begin{equation}\label{eq:chi_model}
\chi^2(\vec{\theta}_{Model}^{hyp}),~~\text{with}~n_i(\vec{\theta}_{Model}^{true})~\text{or}~n_i(\vec{\theta}_{OSC}^{true}).
\end{equation}
%
We note that the minimum of $\chi^2$ in the whole parameter space ($\chi^2_{min.}$) may not be $0$. Therefore, to get the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})\equiv \chi^2(\vec{\theta}_{Model}^{hyp})-\chi^2_{min.}$, instead of $\chi^2(\vec{\theta}_{Model}^{hyp})$ itself. By varying different hypotheses $\vec{\theta}_{Model}^{hyp}$, we will obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})$.

The user can also study how well a flavour symmetry model explains the computed data, or predict whether the simulated experiment can exclude this model or not. In other words, the user studies the minimum of $\chi^2$ for the flavour symmetry model $\vec{\theta}_{Model}$ as a hypothesis, by assuming different true oscillation values, \textit{i.e.}~different $\vec{\theta}^{true}_{OSC}$. To do so, one can compute the same statistical quantity Eq.~(\ref{eq:chi_model}), while the true spectrum is varied with different true values $\vec{\theta}_{OSC}^{true}$. All model parameters are allowed to be varied with the user-defined prior.
%
Finally, the user might adopt Wilk's theorem to interpret results~\cite{Wilks:1938dza}. When we compare nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed as a $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters.

In following two sections, we will present examples to demonstrate how the user can do with \textbf{FaSE-GLoBES} to constrain the model parameter and to exclude a model by the simulated experiment configuration.

@@

\textbf{FaSE-GloBES} can be used to study how model parameters are constrained by simulated neutrino oscillation experiments as we introduced in Sec.~\ref{sec:chi-squared}. We take \textit{the tri-direct littlest seesaw} (TDLS)~\cite{King:2013iva,King:2015dvf,King:2016yvg} as an example. In this model, the light left-handed Majorana neutrino mass matrix is given by
\begin{equation}
\label{eq:mnu}  m_{\nu}=m_{a}\begin{pmatrix}
 1 &~ \omega  &~ \omega ^2 \\
 \omega  &~ \omega ^2 &~ 1 \\
 \omega ^2 &~ 1 &~ \omega  \\
\end{pmatrix}+e^{i\eta}m_{s}
\begin{pmatrix}
 1 &~  x &~  x \\
 x &~ x^2 &~ x^2 \\
 x &~ x^2 &~ x^2 \\
\end{pmatrix}\,,
\end{equation}
where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters to be constrained by simulated data. We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FaSE-GLoBES}. Therefore, the restrictions in this model are $m_a>0$ and $r>0$.
%\begin{figure}[!h]
% \flushleft
%\hspace{15mm}\includegraphics[width=0.32\textwidth]{figs/x_eta.pdf}$~~~~~~$\\
%\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_r.pdf}\hspace{-11mm}
% \includegraphics[width=0.32\textwidth]{figs/eta_r.pdf}$~~~~~~$\\
%\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_ma.pdf}\hspace{-11mm}
% \includegraphics[width=0.32\textwidth]{figs/eta_ma.pdf}\hspace{-11mm}
% \includegraphics[width=0.32\textwidth]{figs/r_ma.pdf}
% \caption{\label{fig:model_2D}Precision measurements of any two model parameters at 3$\sigma$ confidence level in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black). True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
%\end{figure}

\begin{figure}[!h]
 %\flushleft
 \centering
\includegraphics[width=0.48\textwidth]{Figs/x_eta.pdf}
 \includegraphics[width=0.48\textwidth]{Figs/theta_phi.pdf}
% \caption{\label{fig:constraint}Precision measurements of two model parameters in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black). True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
 %
  \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw (left) and the warped flavor symmetry (right), with simulated DUNE and MOMENT data. In the left panel, the dot)denotes the prediction by the tri-direct littlest seesaw model with NuFit4.0 results.}
\end{figure}

In left panel of Fig.~\ref{fig:constraint}, we study how parameters $x$ and $\eta$ can be constrained at $3\sigma$ by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea} and DUNE experiment. 
%We input the model by giving model parameters as functions of standard oscillation parameters Eq.~(\ref{eq:modelofOSC}). 
Parameters $r$ and $ma$ are varied with the prior that is given in standard oscillation parameters, according to the global-fit result NuFit4.0. 
%The code for this example is provided as \textbf{x\_eta.c} in the \textbf{FaSE} distribution.

@@

To show the generality of \textbf{FaSE-GLoBES}, we also present the similar result for another model -- \textit{the warped flavor symmetry} (WFS)~\cite{Chen:2015jta}. This model predicts further simplified correlations that the standard oscillation parameters including mixing angles and the CP phase are functions of only two model parameters $\theta_\nu$ and $\phi_\nu$,
\begin{align}\label{eq:WFS}
\sin^2\theta_{12}&=\frac{1}{2-\sin2\theta_{\nu}\cos\phi_\nu},\nonumber\\
\sin^2\theta_{13}&=\frac{1}{3}(1+\sin2\theta_\nu\cos\phi_\nu),\nonumber\\
\sin^2\theta_{23}&=\frac{1-\sin2\theta_\nu\sin(\pi/6-\phi_\nu)}{2-\sin2\theta_\nu\cos\phi_\nu},\nonumber\\
J_{CP}&=-\frac{1}{6\sqrt{3}}\cos2\theta_\nu.
\end{align}
The constraint of $\theta_\nu$ and $\phi_\nu$ for DUNE and MOMENT is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NuFit 4.0 result as the true values $(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$. To reproduce the result shown in \cite{Chatterjee:2017xkb}, we do not include any priors. More details about these codes are presented in the user manual.

@@

\begin{figure}[!h]
 \centering
\includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_DUNE_MOMENT.pdf}
\includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_WFS.pdf}
\caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour at $99\%$ C.L. on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS (left) and of WFS (right) with DUNE and MOMENT. In the left panel, the star (dot) denotes the prediction by the tri-direct littlest seesaw model with NuFit4.0 results (best fit of NuFit4.0).}
%\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid). The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results. The black dot denotes the best fit of NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$), while the star is the prediction by the tri-direct littlest seesaw model with NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)\sim(36.25^\circ,~8.63^\circ,~47^\circ,~279^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
\end{figure}

We can also study on whether a neutrino mass model is excluded or not, assuming different true values for oscillation parameters. In this example, we present testing sub-models of TDLS in various true values of $\theta_{23}$ and $\delta$. We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior Eq.~(\ref{eq:prior}) according to NuFit4.0 results. Two parameters $x$ and $\eta$ are fixed at the best fit. In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code. 
%
We present this result in the left panel of Fig.~\ref{fig:th23_delta}. We further show the generality of \textbf{FaSE-GLoBES} by demonstrating the similar result for another model -- WFS Eq.~(\ref{eq:WFS}) for DUNE and MOMENT, in right panel of Fig.~\ref{fig:th23_delta}. In this result, two mass-squared differences are fixed at the true values without including any priors.
%
%As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the {\color{blue}assumed} true theory {\color{blue}($\vec{\theta}^{true}_{OSC}$)} and the hypothesis {\color{blue}($\vec{\theta}^{hyp}_{Model}$)}, \texttt{dof}. 
%{\color{blue}`The assumed true theory' here means that the oscillation parameters assumed for predicting the true event spectrum.} \textcolor{red}{[JT: what is the meaning of the true theory?]} 
%Here the number \texttt{dof} is $2$. 
%And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}. \textcolor{red}{[I don't understand this sentence.]} 
More details are presented in the user manual. 
%The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
